---
title: "mTurk_Main_Analyses_updated_full_models"
output:
  rmarkdown::pdf_document:
    extra_dependencies: ["float"]
    #fig_caption: yes        
#   includes:  
#      in_header: preamble.tex
header-includes:
 \usepackage{placeins}
 \usepackage{array}
 \usepackage{longtable}
 \usepackage{wrapfig}
 \usepackage{float}
 \floatplacement{figure}{H}
  # \newcommand\textstyleStrongEmphasis[1]{\textbf{#1}}
  # \makeatletter
  # \newcommand\arraybslash{\let\\\@arraycr}
---

```{r}
#Info about R versioning
#platform       aarch64-apple-darwin20      
# arch           aarch64                     
# os             darwin20                    
# system         aarch64, darwin20           
# status                                     
# major          4                           
# minor          2.2                         
# year           2022                        
# month          10                          
# day            31                          
# svn rev        83211                       
# language       R                           
# version.string R version 4.2.2 (2022-10-31)
# nickname       Innocent and Trusting   
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
```

## add in the income and education factors (show associations with healthy/tasty ratings)

```{r, include=FALSE}
library(tidyr)
library(ggplot2)
library(dplyr)
library(lmerTest)
library(lme4)
library(readxl)
library(cowplot)
library(data.table)
library(readxl)
library(matrixTests)
library(ggpubr)
library(rstatix)
library(afex)
library(emmeans)
library(forcats)
library(sjPlot)
library(polycor)
library(parameters)
library(knitr)
library(psych)
library(interactions)
library(ggrepel)
library(car)
library(ppcor)
library(GGally)
library(ggrain)
library(ggguides)
```


## These analyses describe the demographic characteristics associated with variation in food choice

## Demographic characteristics of interest are: age, gender, cognitive restraint, bmi.


```{r, include=FALSE}
dat <- read.csv("mTURK_July2025.csv")
source("cleanup.R")
dat <- subset(dat,!is.na(dat$education))
t <- subset(t,!is.na(t$education))
```

# First, look at how the demographic factors of interest are related to each other
```{r, results="asis", warnings=FALSE, message=FALSE, echo=FALSE}
t <- function(x){
val <- t.test(demo[[x]]~demo$gender)
return(val$statistic)
}

w <- function(x){
val <- wilcox.test(demo[[x]]~demo$gender)
return(val$statistic)
}

demo <- single %>%
dplyr::select(subjectId, age2, bmi, gender, s.cognitive.restraint, income,education)

cont <- c("age2", "bmi", "s.cognitive.restraint")
ord <- c("income","education")

cors_cont <- demo %>% dplyr::select(cont) %>% cor(method="pearson")
cors_ord <- demo %>% dplyr::select(cont,ord) %>% cor(method="spearman")
cors_ord[1:3,1:3] <- cors_cont[1:3,1:3]
cors_ord <- data.frame(cors_ord)
cors_ord$gender <- ""
cors_ord$gender[1:3] <- sapply(cont, t)
cors_ord$gender[4:5] <- sapply(ord, w)

#cors_ord[lower.tri(cors_ord)] <- 0

print("Table to show association between different demographic characteristics")
print(knitr::kable(cors_ord))
```
```{r}
demo <- single %>%
dplyr::select(age2, gender,bmi, s.cognitive.restraint)
names <- c("Age (years)", "Gender","BMI kg/m^2", "Cognitive Restraint")
for(i in 1:4){
demo$col <- demo[[i]]
p <- (ggplot(demo,aes(x=col)) + geom_histogram(stat="count") + xlab(names[i]))
if(i==3){p <- (ggplot(demo,aes(x=col)) + geom_histogram(binwidth = 3) + xlab(names[i]))}

if(i==1){p <- ggplot(demo,aes(x=col)) + geom_histogram(stat="count") + xlab(names[i]) + scale_x_continuous(breaks=c(0,4,7,10),labels=c("18-25","36-40","51-55","71-75"))}

p <- p + theme_classic2() + ylab("Count") + theme(text = element_text(size=20))
assign(paste0("p",i),p)
}


# PNAS Figure 2 - distribution of key variables (dimensions match the version
# currently embedded in the manuscript)
png("results/Figure2.png", width = 1680, height = 429)
cowplot::plot_grid(p1,p2,p3,p4,nrow=1)
dev.off()

cowplot::plot_grid(p1,p2,p3,p4,nrow=1)
```

# Look at association between choice and three main components for foods: tastiness, healthiness, umami 


# People prefer tastier, less healthy and more savory foods 


```{r, echo=FALSE,results="asis", warnings=FALSE, message=FALSE}

#Now binarize choice
cat("\n\n\\newpage\n")
dat$choice.bin <- ifelse(dat$choice.rating<5,0,1)
dat$choice.bin <- ifelse(dat$choice.rating==5,NA,dat$choice.bin)


##I think for plotting purposes it is nicer to do it by food
avg <- dat %>% group_by(stimulus) %>% summarize_at(c("choice.rating","Healthiness","Tastiness","Umami"),mean,na.rm=TRUE)

avg_count <- dat %>% group_by(stimulus,choice.bin) %>% dplyr::count()
avg_count <- subset(avg_count,!is.na(avg_count$choice.bin))
avg_count <- avg_count %>% pivot_wider("stimulus",names_from=2,values_from=3)
avg_count$prop_choice <- avg_count$`1`/(avg_count$`1`+avg_count$`0`)

avg <- merge(avg,avg_count,by="stimulus")

cat("\n\n\\newpage\n")

BU <- avg

i <- 1
colors <- c("#92D895","sandybrown", "plum")
for(food in c("Healthiness","Tastiness","Umami")){

##missing some foods  
  
labels <- c("kitkat","pizza","strawberries","lox","rice cakes","broccoli","trailmix","skittles")

avg$attribute <- avg[[food]]
avg$label <- ifelse(avg$stimulus %in% labels, avg$stimulus,"")
col_plot <- colors[i]
line_m <- ifelse(i<2.5,"y~x","y ~ x + I(x^2)")
p <- (ggplot(avg, aes(x=attribute,y=prop_choice)) + geom_point(size=4,color=col_plot,fill=col_plot,alpha=0.6) + geom_smooth(method="lm",formula=line_m,size=2,color=col_plot,fill=col_plot,alpha=0.6) + scale_alpha_identity() + ylab("Proportion of selections") + xlab(food) + ylim(0,1) + xlim(-2,2) + ggtitle(food) + geom_text(aes(label=label),nudge_x = 0.1, fontface = "bold",size=6))
ph <- p + theme_blank() + theme(axis.line.x=element_line(color="black",size=2),axis.line.y=element_line(color="black",size=2),text = element_text(size=24), plot.title = element_text(color=col_plot, size=24,face="bold",hjust = .5))

assign(paste0("p",i),ph)
i <- i+1
}

png("results/Figure1.png", width = 1500, height = 500)
cowplot::plot_grid(p1,p2,p3, nrow=1)
dev.off()

```
# Summary of choices across all individuals for alternate (i.e., non neutral food choices), healthy choices, high/low-fat choices, RT for SC choices


```{r, echo=FALSE,results="asis", warnings=FALSE, message=FALSE, include=TRUE}
# check linearity of Umami - non-linear effect adds little predictive power 
# regressing out taste and health = linear effect of Umami on choice preference

dat$Umami2 <- dat$Umami^2 
fit2 <- glmer(choice.bin ~ Healthiness + Tastiness + Umami  + (1|stimulus) + (1 + Healthiness + Tastiness + Umami   | subjectId), data=dat, family="binomial", control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print("prediction of choice")
model_parameters(fit2,keep =c("Healthiness", "Tastiness","Umami"), effects = "fixed") %>% print_md()

fit1 <- glmer(choice.bin ~ Healthiness + Tastiness + Umami + Umami2 + (1|stimulus) + (1 + Healthiness + Tastiness + Umami + Umami2 | subjectId), data=dat, family="binomial", control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print("prediction of choice - with quadratic Umami term")
model_parameters(fit1,keep =c("Healthiness", "Tastiness","Umami"), effects = "fixed") %>% print_md()

anova(fit2,fit1)


```

## RT analysis
```{r, echo=FALSE,results="asis", warnings=FALSE, message=FALSE, include=TRUE}
dat$choice2 <- dat$choice.rating^2
modRT <- lmer(choice.rt.unscale ~ choice.rating + choice2 + (1 + choice.rating + choice2|subjectId) + (1|stimulus),data=dat, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print(model_parameters(modRT) %>% print_md())

dat$cat_choice <- cut(dat$choice.rating, 
                   breaks=c(seq(0,10,1)), 
                   labels=c(as.character(seq(1,10,1))))

rt <- dat %>% group_by(cat_choice) %>% summarise_at("choice.rt.unscale",mean,na.rm=TRUE)
rt <- subset(rt,!is.na(rt$cat_choice))
ggplot(rt,aes(x=cat_choice,y=choice.rt.unscale)) + geom_bar(stat="identity")

dat$neut.Umami2 <- dat$neut.Umami^2
dat$Umami_diff <- dat$Umami - dat$neut.Umami
dat$Umami2_diff <- dat$Umami2 - dat$neut.Umami2
dat$Healthiness_diff <- dat$Healthiness - dat$neut.Healthiness
dat$Tastiness_diff <- dat$Tastiness - dat$neut.Tastiness


modRTdiff <- lmer(choice.rt.unscale ~ Umami_diff + Umami2_diff + Tastiness_diff + Healthiness_diff + (1 + Umami_diff + Umami2_diff + Tastiness_diff + Healthiness_diff|subjectId) + (1|stimulus),data=dat, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print(model_parameters(modRTdiff) %>% print_md())

ggplot(dat, aes(x=choice.rating,y=choice.rt)) + geom_smooth()
```


# associations with tastiness, healthy, HL-fat, RT, non neutral choice per demo char

```{r, echo=FALSE,results="asis", warnings=FALSE, message=FALSE, include=TRUE}

tab_means <- health_select %>% unique() %>% summarize_at(c(2:8),c(mean,sd),na.rm=TRUE)
table_means <- data.frame()
for(i in 1:7){
val <- paste0(round(tab_means[i],3)," (",round(tab_means[i+7],3),")")
row_val <- as.data.frame(c(gsub("_fn1","", colnames(tab_means[i])),val))
row_val <- transpose(row_val)
colnames(row_val) <- c("var","mean (SD)")
table_means <- rbind(table_means,row_val)              
}

print(table_means)
```


# Generate plots using two-stage estimation (beta coefficients for each individual)
```{r, echo=FALSE,results="asis", warnings=FALSE, message=FALSE}
coef <- coef(fit1)$subjectId
coef$subjectId <- rownames(coef)
colnames(coef) <- c( "(Intercept)","Healthiness_beta","Tastiness_beta","Umami_beta","Umami_quadratic_beta","subjectId" )
single <- merge(single, coef,by="subjectId")

```


```{r, echo=FALSE,results="asis", warnings=FALSE, message=FALSE}
# These are simple associations of demo factors with influence of healthiness, tastiness, umami on choice


cat("\n\n\\newpage\n")
preds <- c("age2", "gender", "bmi","s.cognitive.restraint") #,"education","income")
pred.names <- c("Age (years)","Gender","BMI (kg/m^2)","Cognitive Restraint","Cognitive Restraint x BMI")
colour <- c("sandybrown","#92D895","plum","maroon")
titles <- c("Tastiness","Healthiness","Umami","Umami_quadratic")
outcomes <- c("fit.t","fit.h","fit.u")
outcomes <- c("Tastiness_beta","Healthiness_beta","Umami_beta","Umami_quadratic_beta")
outcome.names <- c("Tastiness Effect","Healthiness Effect","Umami Effect","Umami Effect (quadratic)")

a <- c(-0.5,5)
b <- c(-1.5,1.6)
c <- c(-1.5,1.6)
d <- c(-0.5,0.5)

breaks_a <- seq(-0.5,5,1)
breaks_b <- seq(-1,1.5,0.5)
breaks_c <- seq(-1,1.5,0.5)
breaks_d <- seq(-0.5,0.5,0.2)

lims <- list(a,b,c,d)
breaks <- list(breaks_a,breaks_b,breaks_c,breaks_d)


TAB_lm <- data.frame()
i <- 1

#
for(out in outcomes){
col_out <- colour[i]
single$out <- single[[out]]

j <- 1

for(pred in preds){
single$pred <- single[[pred]]
predname <- pred.names[j]
title <- ""
cat("\n\n\\newpage\n")


p <- plot_template(single,pred = pred,out=out,xlabel = predname,col_out=col_out,ylims=lims[i][[1]],ybreaks=c(breaks[[i]]),title="",yname="Beta")
assign(paste0("p",j),p)


p <- ggplot() + 
  annotate("text", x = 4, y = 25, size=12, label = outcome.names[[i]],color=col_out,fontface =2) + 
  theme_void()
assign(paste0(titles[[i]],"_p"),p)
j <- j+1
}
assign(paste0("plot",i),cowplot::plot_grid(p1,p2,p3,p4,nrow=1,align="vh"))
i <- i+1
}

png("results/Figure3.png", width = 1500, height = 1600)
cowplot::plot_grid(Tastiness_p,plot1,Healthiness_p,plot2,Umami_p,plot3,Umami_quadratic_p, plot4,nrow=8,rel_heights =c(0.2,1,0.2,1,0.2,1,0.2,1))
dev.off()

```


```{r}
##interaction plots - median split with BMI

single$bmi_cat <- ifelse(single$bmi > 26.56,1,0)

a <- c(1.5,3)
b <- c(-0.3,0.6)
c <- c(-0.3,.6)
d <- c(-0.1,.1)

lims <- list(a,b,c,d)

j <- 1
for(out in outcomes){
cat("\n\n\\newpage\n")
tit=""
col_out <- colour[j]
single$out <- single[[out]]

xbreaks <- range(round(single$s.cognitive.restraint,0),na.rm=TRUE)
labs <- xbreaks

p <- ggplot(single,aes(x=s.cognitive.restraint,y=out,group=bmi_cat,alpha=bmi_cat)) + geom_smooth(method = "lm",size=3,aes(alpha=bmi_cat),color=col_out,fill=col_out) + scale_alpha_continuous(range=c(0.3,0.8))  + ggtitle(tit) + coord_cartesian(ylim = c(lims[[j]])) + scale_x_continuous(breaks = xbreaks, labels = labs) + xlab("Cognitive Restraint") + ylab("Beta")
p <- p + theme_blank() + theme(axis.line.x=element_line(color="black",size=1),axis.line.y=element_line(color="black",size=1),text = element_text(size=28),plot.title = element_text(color="black", size=14,face="bold",hjust = .5),legend.position = "none")
assign(paste0("p",j),p)
j <- j+1
}
# height raised from 400 to match the aspect ratio of the version currently
# embedded in the manuscript (2014 x 588), so it drops in without distortion
png("results/Figure4.png", width = 2000, height = 584)
cowplot::plot_grid(Tastiness_p,Healthiness_p,Umami_p,Umami_quadratic_p, p1,p2,p3,p4,nrow=2,rel_heights =c(0.1,1),ncol = 4)
dev.off()

```

## In fully adjusted models, all demographic characteristics are included
# greater influence of health on choice for: higher restraint, lower bmi, older age
# greater influence of taste for: older age, female, lower restraint
# greater preference for savory for: lower bmi
```{r, echo=FALSE,results="asis", warnings=FALSE, message=FALSE}

## full models
TAB <- data.frame()

cat("\n\n\\pagebreak\n")
print("Do age, bmi, cognitive restraint and gender independently predict influence of healthiness, tastiness, umami?")


form <- paste0("choice.bin ~  (1+ Healthiness + Tastiness + (Umami) + Umami2| subjectId) + Healthiness*s.cognitive.restraint_scale + Healthiness*bmi_scale+ Healthiness*age2_scale+Healthiness*gender_num_scale +Healthiness*income_scale + Umami*s.cognitive.restraint_scale + Umami*bmi_scale+ Umami*age2_scale+Umami*gender_num_scale  + Umami*income_scale + Tastiness*s.cognitive.restraint_scale + Tastiness*bmi_scale+ Tastiness*age2_scale+Tastiness*gender_num_scale + Tastiness*income_scale + Umami2*s.cognitive.restraint_scale + Umami2*bmi_scale+ Umami2*age2_scale+Umami2*gender_num_scale + education_scale*Umami + education_scale*Tastiness + education_scale*Healthiness + (1|stimulus)")
mod <- glmer(form,data=dat, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE),family="binomial")
print(parameters::model_parameters(mod) %>% print_md())

form <- paste0("choice.bin ~  (1+ Tastiness + Healthiness + (Umami) + Umami2| subjectId) + Tastiness + Healthiness + (Umami) + Umami2 + Tastiness*age2_scale+Tastiness*gender_num_scale + Tastiness*bmi_scale*s.cognitive.restraint_scale +  Tastiness*income_scale +  Tastiness*education_scale + Healthiness*age2_scale+Healthiness*gender_num_scale + Healthiness*bmi_scale*s.cognitive.restraint_scale +  Healthiness*income_scale +  Healthiness*education_scale + Umami*age2_scale+Umami*gender_num_scale + Umami*bmi_scale*s.cognitive.restraint_scale +  Umami*income_scale +  Umami*education_scale + Umami2*age2_scale+Umami2*gender_num_scale + Umami2*bmi_scale*s.cognitive.restraint_scale +  Umami2*income_scale +  Umami2*education_scale + (1|stimulus)")
mod_int1 <- glmer(form,data=dat, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE),family="binomial")
print(parameters::model_parameters(mod_int1) %>% print_md())

print(anova(mod,mod_int1))

```

```{r, echo=FALSE,results="asis", warnings=FALSE, message=FALSE, include=TRUE}
# check linearity of Umami - non-linear effect adds little predictive power 
# regressing out taste and health = linear effect of Umami on choice preference

fit_rt <- lmer(choice.rt.unscale ~ Healthiness + Tastiness + Umami + (1|stimulus) + (1 + Healthiness + Tastiness + Umami | subjectId), data=dat, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print("prediction of choice")
model_parameters(fit_rt,keep =c("Healthiness", "Tastiness","Umami"), effects = "fixed") %>% print_md()

dat$diff_taste <- dat$Tastiness - dat$neut.Tastiness
dat$diff_health <- dat$Healthiness - dat$neut.Healthiness
dat$diff_umami <- dat$Umami - dat$neut.Umami

fit_rt_diff <- lmer(choice.rt.unscale ~ diff_health + diff_taste + diff_umami + (1|stimulus) + (1 + diff_health + diff_taste + diff_umami | subjectId), data=dat, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print("prediction of choice")
model_parameters(fit_rt_diff,keep =c("Healthiness", "Tastiness","Umami"), effects = "fixed") %>% print_md()

ggplot(dat,aes(x=diff_taste,y=choice.rt.unscale)) + geom_smooth(color="sandybrown") + geom_smooth(data=dat,aes(x=diff_health,y=choice.rt.unscale),color="#92D895") + geom_smooth(data=dat,aes(x=diff_umami,y=choice.rt.unscale),color="plum")


fit_rt_c <- lmer(choice.rt.unscale ~ choice.rating + choice2 + (1|stimulus) + (1 + choice.rating +choice2 | subjectId), data=dat, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print("prediction of choice")
model_parameters(fit_rt_c,effects = "fixed") %>% print_md()



```


```{r,echo=TRUE}
cat("\n\n\\newpage\n")
preds <- c("age2", "gender","bmi", "s.cognitive.restraint") #,"education","income")
pred.names <- c("Age","Gender","BMI","Cognitive Restraint")

titles <- c("Healthy Choice Proportion")
outcomes <- c("healthy.choice.prop")

i <- 1
for(pred in preds){
single$pred <- single[[pred]]
xlabel <- pred.names[i]

title <- ""
ylims=c(0,1)
ybreaks=c(0,.25,.50,.75,1.00)
ylabels=c("0",".25",".50",".75","1")
yname="Healthy Choice Proportion"
if(i ==1){tit=title}
else{tit=""}
cat("\n\n\\newpage\n")

out <- "healthy.choice.prop"
single$out <- single$healthy.choice.prop


p <- plot_template(single,pred = pred,out=out,xlabel = xlabel,col_out="#FDD262",ylims=ylims,ybreaks=ybreaks,title=title,yname=yname)


assign(paste0("p",i),p)
print(p)
i <- i+1
}

png("results/Figure5.png", width = 2000, height = 600)
cowplot::plot_grid(p1,p2,p3,p4,nrow=1,align="vh")
dev.off()
```


```{r}
print("full model - healthy choices")
form <- paste0("healthy.choice.prop ~ gender_num_scale + age2_scale + s.cognitive.restraint_scale + bmi_scale + income_scale + education_scale")
mod <- lm(form, single)
print(model_parameters(mod) %>% print_md())
```

## How does number of self-control trials vary with variables of interest?
# Males  = greater number of SC trials
# Greater restraint  = fewer SC trials
```{r, echo = FALSE, results="asis", warnings=FALSE, message=FALSE}
print("full model - predict number of sc trials")
form <- paste0("n.sctrial_fac ~ gender_num_scale + age2_scale + s.cognitive.restraint_scale + bmi_scale + income_scale + education_scale")
mod <- lm(form, single)
print(model_parameters(mod) %>% print_md())

print("full model to predict self-control")
form <- paste0("sc.rat.factor ~ gender_num_scale + age2_scale + s.cognitive.restraint_scale + bmi_scale + income_scale + education_scale + n.sctrial_fac")
mod <- lm(form, single)
print(model_parameters(mod) %>% print_md())

form <- paste0("sc.rat.factor ~ n.sctrial_fac*(gender_num_scale  + age2_scale + s.cognitive.restraint_scale + bmi_scale + income_scale + education_scale)")
mod <- lm(form, single)
print(model_parameters(mod) %>% print_md())


```


```{r}
form <- paste0("n.sctrial_fac ~ gender_num_scale + age2_scale + s.cognitive.restraint_scale + bmi_scale + income_scale + education_scale")
mod <- lm(form, single)
print(model_parameters(mod) %>% print_md())
```

```{r}
cat("\n\n\\newpage\n")
preds <- c("age2","gender", "bmi", "s.cognitive.restraint") #,"education","income")
pred.names <- c("Age","Gender","BMI","Cognitive Restraint")
colour <- c("darkblue","#85D4E3")
titles <- c("Number of Conflict Trials","Self-Control Success")

outcomes <- c("n.sctrial_fac","sc.rat.factor")


i <- 1
for(out in outcomes){
j <- 1
col_out <- colour[i]
yname <- titles[i]
for(pred in preds){
single$pred <- single[[pred]]
xlabel <- pred.names[j]  
title <-""

if(i==1){ylims=c(0,40)}else{ylims=c(0,1)}
if(i==1){ybreaks=c(0,10,20,30,40);ylabels=c("0","10","20","30","40")}else{ybreaks=c(0,.25,.50,.75,1.00);ylabels=c("0",".25",".50",".75","1")}

cat("\n\n\\newpage\n")

single$out <- single[[out]]
p <- plot_template(single,pred = pred,out=out,xlabel = xlabel,col_out=col_out,ylims=ylims,ybreaks=ybreaks,title=title,yname=yname)
assign(paste0("p",j),p)

p <- ggplot() + 
  annotate("text", x = 4, y = 25, size=12, label = titles[[i]],color=col_out,fontface =2) + 
  theme_void()
assign(paste0(titles[[i]],"_p"),p)

j <- j+1


}
assign(paste0("plot",i),cowplot::plot_grid(p1,p2,p3,p4,nrow=1,align="vh"))
i <- i+1
}


png("results/Figure6.png", width = 1500, height = 1000)
cowplot::plot_grid(`Number of Conflict Trials_p`,plot1,`Self-Control Success_p`,plot2,nrow=4,rel_heights=c(0.2,1,0.2,1))
dev.off()
```


```{r, echo=FALSE, results="asis", warnings=FALSE, message=FALSE}
i <- 1
colors <- c("#92D895", "plum")
for(food in c("Healthiness","Umami")){

labels <- c("kitkat","pizza","strawberries","lox","rice cakes","broccoli","trailmix","skittles")

avg$attribute <- avg[[food]]

avg$label <- ifelse(avg$stimulus %in% labels, avg$stimulus,"")

col_plot <- colors[i]
line_m <- ifelse(i<1.5,"y~x","y ~ x + I(x^2)")
p <- (ggplot(avg, aes(x=attribute,y=Tastiness)) + geom_point(size=4,color=col_plot,fill=col_plot,alpha=0.6) + geom_smooth(method="lm",formula=line_m,size=2,color=col_plot,fill=col_plot,alpha=0.6) + scale_alpha_identity() + ylab("Tastiness") + xlab(food) + ylim(-0.6,1) + xlim(-2,2) + ggtitle(food) + geom_text(aes(label=label), fontface = "bold"))
ph <- p + theme_blank() + theme(axis.line.x=element_line(color="black",size=2),axis.line.y=element_line(color="black",size=2),text = element_text(size=16), plot.title = element_text(color=col_plot, size=24,face="bold",hjust = .5))

assign(paste0("p",i),ph)
i <- i+1
}

cowplot::plot_grid(p1,p2,nrow=1)


avg <- dat %>% group_by(stimulus) %>% summarize_at(c("choice.rating","Healthiness","Tastiness","Umami"),mean,na.rm=TRUE)
avg$label <- ifelse(avg$stimulus %in% labels, avg$stimulus,"")
print("here is plot of tastiness residuals on healthiness")
mod <- lm(Tastiness ~ Umami,avg)
avg$res_tu <- resid(mod)
p <- (ggplot(avg, aes(x=Umami,y=res_tu)) + geom_point(size=3,color="bisque4",fill="bisque4",alpha=0.4) + geom_smooth(method="lm",formula="y ~ x + I(x^2)", size=2,color="bisque4",fill="bisque4",alpha=0.4) + geom_text(aes(label=label)))
print(p + theme_blank() + theme(axis.line.x=element_line(color="black",size=2),axis.line.y=element_line(color="black",size=2),text = element_text(size=16), plot.title = element_text(color=col_plot, size=24,face="bold",hjust = .5))
)

```

```{r, echo=FALSE, results="asis", warnings=FALSE, message=FALSE,fig.show='hold'}
dat$Umami2 <- dat$Umami^2
fit_th_quad <- lmer(Tastiness ~ Healthiness +  Umami + Umami2 + (1|stimulus) + (1 + Healthiness +  Umami + Umami2|subjectId), data=dat, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))

summary(fit_th_quad)
model_parameters(fit_th_quad) %>% print()


fit_th <- lmer(Tastiness ~ Healthiness +  Umami  + (1|stimulus) + (1 + Healthiness +  Umami |subjectId), data=dat, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))

coef_th <- coef(fit_th_quad)$subjectId
coef_th$subjectId <- rownames(coef_th)
colnames(coef_th) <- c( "Intercept_taste","Health_taste_beta","Umami_taste_beta","Umami_taste_quadratic_beta","subjectId" )
single <- merge(single, coef_th,by="subjectId")
cat("\n\n\\newpage\n")
```

```{r}
cat("\n\n\\newpage\n")

print("Maximally adjusted")
form <- paste0("Tastiness ~  (1 + Healthiness + Umami + Umami2 | subjectId) + Healthiness*age2_scale+Healthiness*gender_num_scale + Healthiness*income_scale + Healthiness*education_scale  + Umami*income_scale + Umami*education_scale + Umami*age2_scale+Umami*gender_num_scale +   Umami*s.cognitive.restraint_scale + Umami*bmi_scale+  Healthiness*s.cognitive.restraint_scale + Healthiness*bmi_scale + Umami2*income_scale + Umami2*education_scale + Umami2*age2_scale+Umami2*gender_num_scale + Umami2*s.cognitive.restraint_scale + Umami2*bmi_scale +  (1|stimulus)")
mod_tuh <- lmer(form,data=dat, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print(parameters::model_parameters(mod_tuh) %>% print_md())

```

```{r}
cat("\n\n\\newpage\n")
preds <- c("age2", "gender","bmi","s.cognitive.restraint") #,"education","income")
pred.names <- c("Age","Gender","BMI","Cognitive Restraint")
colour <- c("#92D895","plum","maroon")
titles <- c("Healthiness","Umami","Umami2")

outcomes <- c("Health_taste_beta","Umami_taste_beta","Umami_taste_quadratic_beta")
outcome_names <- c("Healthiness Effect","Umami Effect (linear)","Umami Effect (quadratic)")

lims <- c(-1,1)

ybreaks=c(-1.0,-0.5,0.0,0.5,1.0)
ylabels=c("-1.0","-0.5","0","0.5","1.0")

ybreaks_u=c(-0.6,-0.3,0.0,0.3,0.6)
lims_u <- c(-0.6,0.6)
ylabels_u=c("-0.75","-0.25","0","0.25","0.75")

i <- 1
for(out in outcomes){
if(i > 1) {ybreaks <- ybreaks_u; lims <- lims_u}
col_out <- colour[i]
single$out <- single[[out]]
j <- 1
title <- ""

cat("\n\n\\newpage\n")
for(pred in preds){
single$pred <- single[[pred]]
predname <- pred.names[j]

p <- plot_template(single,pred = pred,out=out,xlabel = predname,col_out=col_out,ylims=lims,ybreaks=ybreaks,title=title,yname="Beta")
assign(paste0("p",j),p)



p <- ggplot() + 
  annotate("text", x = 4, y = 25, size=12, label = outcome_names[[i]],color=col_out,fontface =2) + 
  theme_void()
assign(paste0(titles[[i]],"_p"),p)
j <- j+1

}
assign(paste0("plot",i),cowplot::plot_grid(p1,p2,p3,p4,nrow=1))
i <- i+1
}


png("results/Figure7.png", width = 1500, height = 1200)
cowplot::plot_grid(Healthiness_p,plot1,Umami_p,plot2,Umami2_p,plot3,nrow=6,rel_heights =c(0.2,1,0.2,1,0.2,1))
dev.off()
```



# here looking at hXt correlation and SC, with selection of healthier foods, high-fat foods, low-fat foods, influence of health on choice, and SC RTs
```{r, echo = FALSE, results="asis", warnings=FALSE, message=FALSE}

form <- "healthy.choice.prop ~ scale(Health_taste_beta,center=TRUE) + scale(sc.rat.factor,center=TRUE)"
mod <- lm(form, single)
cat("\n\n\\newpage\n")
print("healthy choice proportion on Healthiness-Tastiness alignment + self-control success")
print(model_parameters(mod) %>% print_md())

form <- "healthy.choice.prop ~ scale(Umami_taste_beta,center=TRUE)" # #scale(sc.rat.factor,center=TRUE)
mod <- lm(form, single)
cat("\n\n\\newpage\n")
print("healthy choice proportion on Umami-Tastiness alignment")
print(model_parameters(mod) %>% print_md())

form <- "healthy.choice.prop ~ scale(Umami_taste_quadratic_beta,center=TRUE) + scale(Umami_taste_beta,center=TRUE) +  scale(Health_taste_beta,center=TRUE) + scale(sc.rat.factor,center=TRUE)"
mod <- lm(form, single)
cat("\n\n\\newpage\n")
print("healthy choice proportion on all alignment terms + self-control success")
print(model_parameters(mod) %>% print_md())

form <- "healthy.choice.prop ~ scale(Umami_taste_quadratic_beta,center=TRUE) + scale(Umami_taste_beta,center=TRUE)"
mod <- lm(form, single)
cat("\n\n\\newpage\n")
print("healthy choice proportion on Umami-Tastiness alignment (linear + quadratic)")
print(model_parameters(mod) %>% print_md())

cor.test(single$sc.rat.factor,single$Health_taste_beta)
```

```{r}

xbreaks <- range(round(single$sc.rat.factor,0),na.rm=TRUE)
labs <- xbreaks
j <- 3
ylims=c(0,1)
ybreaks=c(0,.25,.50,.75,1.00)
ylabels=c("0",".25",".50",".75","1")

p1 <- plot_template(single,"sc.rat.factor","healthy.choice.prop",col_out = "#FDD262",ylims = ylims,ybreaks = ybreaks,yname = "Proportion of healthy choices",xlabel = "Self-Control Success")

p2 <- plot_template(single,"Health_taste_beta","healthy.choice.prop",col_out = "#FDD262",ylims = ylims,ybreaks = ybreaks,yname = "Proportion of healthy choices",xlabel = "Healthiness-Tastiness Beta")

png("results/Figure8.png", width = 750, height = 400)
cowplot::plot_grid(p1,p2,nrow=1)
dev.off()

plot_template(single,"sc.rat.factor","Health_taste_beta",col_out = "#FDD262",ylims = ylims,ybreaks = ybreaks,yname = "Healthiness-Tastiness Beta",xlabel = "Self-Control Success")

```

## RT analysis

## what happens to RT on successful vs unsuccessful self-control trials
## largely effects of cognitive restraint - faster to make healthier choices and to use SC (relative to no SC)
```{r echo=FALSE, message=FALSE, results="asis", warnings=FALSE}
cat("\n\n\\newpage\n")
print("Maximally adjusted models")


## here is regular RT model - compare SC RT and no SC RT over demographic groups
no_sc <- single[,c("subjectId","rt_no_sc","bmi_scale","gender_num_scale", "age2_scale", "s.cognitive.restraint_scale", "income_scale","education_scale")]
sc <- single[,c("subjectId","rt_sc","bmi_scale","gender_num_scale", "age2_scale", "s.cognitive.restraint_scale","income_scale","education_scale")]
colnames(sc)[2] <- "rt"
colnames(no_sc)[2] <- "rt"
sc$trial <- "sc"
no_sc$trial <- "no_sc"

SC_RT <- rbind(sc,no_sc)
modRT <- lmer(rt ~ trial*gender_num_scale + trial*age2_scale + trial*bmi_scale + trial*s.cognitive.restraint_scale + trial*income_scale + trial*education_scale + (1|subjectId),data=SC_RT, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print(model_parameters(modRT) %>% print_md())


modRT <- lmer(rt ~ trial*bmi_scale + trial*s.cognitive.restraint_scale*bmi_scale + trial*age2_scale + trial*gender_num_scale + trial*income_scale + trial*education_scale + (1|subjectId),data=SC_RT, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print(model_parameters(modRT) %>% print_md())



```

## average kcals of reference item do not vary by demographic group


```{r, echo = FALSE, results="asis", warnings=FALSE, message=FALSE,include=FALSE}
# diffs in ref food kcal by demo chars
form <- paste0("neut.Total.kcal ~ gender_num_scale + age2_scale + s.cognitive.restraint_scale + bmi_scale + income_scale + education_scale")
mod <- lm(form, single)
print(model_parameters(mod)) %>% print_md()
```





```{r, echo = FALSE, results="asis", warnings=FALSE, message=FALSE}
cat("\n\n\\newpage\n")
wide_ests <- read.csv("recover_M2_params_withID.csv")

wide_ests <- merge(single, wide_ests,by ="subjectId")
preds <- c("gender", "age2", "bmi", "s.cognitive.restraint")
outcomes <- (wide_ests) %>% dplyr::select(starts_with('true')) %>% colnames()
outcome.names <- c("Choice Boundary","Non-Decision Time","Choice Bias", "Tastiness Beta","Healthiness Beta","Umami Beta")

#wide_ests$time_health.p <- abs(wide_ests$time_health.p)



TV <- data.frame()
for(out in outcomes){
wide_ests$out <- wide_ests[[out]]
m <- lm(out ~ gender_num_scale + age2_scale + s.cognitive.restraint_scale+bmi_scale + income_scale + education_scale,wide_ests)# + income_scale + education_scale,tv_ests)
print(paste0(out," ~ s.cognitive.restraint + bmi + age2 + gender"))
print(model_parameters(m) %>% print_md())
}
```


```{r}
#Figures


preds <- c("age2", "gender", "bmi","s.cognitive.restraint") #,"education","income")
pred.names <- c("Age","Gender","BMI","Cognitive Restraint")
colour <- c()
colours <- c("slateblue2", "lightcoral","sandybrown", "#92D895")
       


fig.names <- c("Choice Boundary","Non-Decision Time","Tastiness Effect","Healthiness Effect")

axislab <- c("Bound","NDT","Beta","Beta")
limits <- list(c(0,4),c(0,2),c(0,2),c(-.5,.5))


TAB_lm <- data.frame()
i <- 1

#
for(out in outcomes[c(1:2,4:5)]){

col_out <- colours[i]
wide_ests$out <- wide_ests[[out]]
ylims <- c(limits[[i]])
y <- axislab[i]
ybreaks=seq(ylims[1],ylims[2],(ylims[2]-ylims[1])/4)
title <-fig.names[i]
j <- 1

for(pred in preds){


if(i ==1){tit=title}
  else{tit=""}
cat("\n\n\\newpage\n")

wide_ests$pred <- wide_ests[[pred]]
predname <- pred.names[j]

p <- plot_template(dataset = wide_ests,pred = pred,out=out,col_out = col_out,title=title,xlabel = predname,ylims=ylims,ybreaks=ybreaks,yname=y)
assign(paste0("p",j),p)
j <- j+1
}
assign(paste0("plot",i),cowplot::plot_grid(p1,p2,p3,p4,nrow=1))
i <- i+1
}

i <- 1
for(out in outcomes[c(1:2,4:5)]){
p <- ggplot() + 
  annotate("text", x = 6, y = 25, size=12, label = fig.names[[i]],color=colours[i],fontface =2) +
  theme_void()
assign(paste0(out,"_p"),p)
i <- i+1
}
#title <- cowplot::plot_grid(,nrow=1)

##int 
# NOTE: every element below is a theme_void() *label* panel, so this figure
# contains four text titles and no data. Left as-is pending a decision on what
# it was meant to show; Figure11_p2 is the figure used in the manuscript.
png("results/Figure9_labels.png", width = 2000, height = 1500)
cowplot::plot_grid(true_b1_p, true_b2_p, true_alpha_p, true_theta_p, nrow=4,rel_heights =c(1,1,1,1))
dev.off()



png("results/Figure9.png", width = 2000, height = 1500)
cowplot::plot_grid(true_b1_p,plot3,true_b2_p,plot4,true_alpha_p,plot1,true_theta_p,plot2, nrow=8,rel_heights =c(0.1,1,0.1,1,0.1,1,0.1,1))
dev.off()
```

```{r, echo = FALSE, results="asis", warnings=FALSE, message=FALSE}
wide_ests <- read.csv("recover_M2_params_withID.csv")

i=1
TV <- data.frame()
for(out in outcomes){
name=outcome.names[i]
wide_ests$inp <- wide_ests[[out]]
wide_ests$out <- wide_ests[[gsub("true","rec",out)]]
c <- corr.test(wide_ests$inp,wide_ests$out)# + income_scale + education_scale,tv_ests)
lab = paste0(name,": r = ",round(c$r,2))

p = (ggplot(wide_ests,aes(x=inp,y=out)) + geom_point()) + geom_smooth(method="lm") + ggtitle(lab) + theme_blank() + theme(axis.line.x=element_line(color="black"), axis.line.y=element_line(color="black")) + xlab("True") + ylab("Recovered") 
assign(paste0(out,"_plt"),p)

i=i+1

}

cowplot::plot_grid(true_b1_plt,true_b2_plt,true_b3_plt,true_alpha_plt,true_theta_plt,true_bias_plt)



```