---
title: "mTurk_Main_Analyses_updated_full_models"
output:
  rmarkdown::pdf_document:
    extra_dependencies: ["float"]
    #fig_caption: yes        
#   includes:  
#      in_header: preamble.tex
header-includes:
 \usepackage{placeins}
 \usepackage{array}
 \usepackage{longtable}
 \usepackage{wrapfig}
 \usepackage{float}
 \floatplacement{figure}{H}
  # \newcommand\textstyleStrongEmphasis[1]{\textbf{#1}}
  # \makeatletter
  # \newcommand\arraybslash{\let\\\@arraycr}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
```

## add in the income and education factors (show associations with healthy/tasty ratings)

```{r, include=FALSE}
library(tidyr)
library(ggplot2)
library(dplyr)
library(lmerTest)
library(lme4)
library(readxl)
library(cowplot)
library(data.table)
library(readxl)
library(matrixTests)
library(ggpubr)
library(rstatix)
library(afex)
library(emmeans)
library(forcats)
library(sjPlot)
library(polycor)
library(parameters)
library(knitr)
library(psych)
library(interactions)
library(ggrepel)
library(car)
library(ppcor)
library(GGally)
library(ggrain)
```


## These analyses describe the demographic characteristics associated with variation in food choice

## Demographic characteristics of interest are: age, gender, cognitive restraint, bmi.


```{r, include=FALSE}
dat <- read.csv("~/Dropbox/mTurk/mTURK_July2025.csv")
source("~/Dropbox/mTurk/cleanup1.R")
dat <- subset(dat,!is.na(dat$education))
t <- subset(t,!is.na(t$education))
```

# First, look at how the demographic factors of interest are related to each other
```{r, results="asis", warnings=FALSE, message=FALSE, echo=FALSE}
t <- function(x){
val <- t.test(demo[[x]]~demo$gender)
return(val$statistic)
}

w <- function(x){
val <- wilcox.test(demo[[x]]~demo$gender)
return(val$statistic)
}

demo <- single %>%
dplyr::select(subjectId, age2, bmi, gender, s.cognitive.restraint, income,education)

cont <- c("age2", "bmi", "s.cognitive.restraint")
ord <- c("income","education")

cors_cont <- demo %>% dplyr::select(cont) %>% cor(method="pearson")
cors_ord <- demo %>% dplyr::select(cont,ord) %>% cor(method="spearman")
cors_ord[1:3,1:3] <- cors_cont[1:3,1:3]
cors_ord <- data.frame(cors_ord)
cors_ord$gender <- ""
cors_ord$gender[1:3] <- sapply(cont, t)
cors_ord$gender[4:5] <- sapply(ord, w)

#cors_ord[lower.tri(cors_ord)] <- 0

print("Table to show association between different demographic characteristics")
print(knitr::kable(cors_ord))
```
```{r}
demo <- single %>%
dplyr::select(age2, gender,bmi, s.cognitive.restraint)
names <- c("Age (years)", "Gender","BMI kg/m^2", "Cognitive Restraint")
for(i in 1:4){
demo$col <- demo[[i]]
p <- (ggplot(demo,aes(x=col)) + geom_histogram(stat="count") + xlab(names[i]))
if(i==3){p <- (ggplot(demo,aes(x=col)) + geom_histogram(binwidth = 3) + xlab(names[i]))}

if(i==1){p <- ggplot(demo,aes(x=col)) + geom_histogram(stat="count") + xlab(names[i]) + scale_x_continuous(breaks=c(0,4,7,10),labels=c("18-25","36-40","51-55","71-75"))}

p <- p + theme_classic2() + ylab("Count") + theme(text = element_text(size=20))
assign(paste0("p",i),p)
}


cowplot::plot_grid(p1,p2,p3,p4,nrow=1)
```


```{r, results="asis", warnings=FALSE, message=FALSE, echo=FALSE}

set_theme(
  title.size = 0.8, axis.textsize = 20,axis.title.size = 20,axis.ticksize.x = 20,
  base = theme(axis.line = element_line(color="black"))
)

demo[,c("age2","s.cognitive.restraint","bmi")] <- sapply(demo[,c("age2","s.cognitive.restraint","bmi")],as.numeric)

#demo[,c("income","education")] <- sapply(demo[,c("income","education")],as.factor)

ordinal <- c("income","education")

demo$gender <- substr(demo$gender,1,1)
demo$gender <- as.factor(demo$gender)
names <- c("Age (years)","bmi (kg/m2)","Gender", "Cognitive restraint (TFEQ)")
labels_age <- c("18-25", "26-30", "31-35", "36-40", "41-45", "46-50", "51-55", "56-60", "61-65", "66-70", "71-75")
demo$age2 <- as.numeric(demo$age2)

for(i in 1:4){
val <- paste0(names[i])
p1 <- ggplot() + 
  annotate("text", x = 4, y = 25, size=5, label = val,angle=90) + 
  theme_void()
var1 <- colnames(cor1)[i]
assign(paste0(var1),p1)

p1 <- ggplot() + 
  annotate("text", x = 4, y = 25, size=5, label = val) + 
  theme_void()
var1 <- colnames(cor1)[i]
assign(paste0(var1,"_h"),p1)

col <- dataframe$cols[dataframe$vars==var1]
for(i in 1:4){
var2 <- rownames(cor1)[i]
name_test <- paste0(var1,var2)
if(var1==var2){
if(class(demo[[var1]])=="numeric"){
p <- ggplot(demo,aes_string(x=var1))+ geom_histogram(stat="count",color="gray",fill="gray") + theme_blank() + xlab("") + theme(axis.text = element_blank(),axis.line.x=element_line(colour = "black"),axis.line.y=element_line(colour = "black"), title=element_text(size=20,hjust = 0.5)) + scale_x_continuous(breaks=range(demo[[var1]]),labels=round(range(demo[[var1]]),1))}
if(class(demo[[var1]])=="factor"){  
p <- ggplot(demo,aes_string(x=var1))+ geom_histogram(stat="count",color="gray",fill="gray") + theme_blank() + xlab("") + theme(axis.text = element_blank(),axis.line.x=element_line(colour = "black"),axis.line.y=element_line(colour = "black"),title=element_text(size=20,hjust = 0.5))}
if(var1 =="age2"){
p <- ggplot(demo,aes_string(x=var1)) + geom_histogram(stat="count",color="gray",fill="gray") + scale_x_discrete(limits=labels_age) + theme_blank() + xlab("") + theme(axis.text = element_blank(),axis.line.x=element_line(colour = "black"),axis.line.y=element_line(colour = "black"), title=element_text(size=20,hjust = 0.5))}
assign(name_test,p)
}

if(!var1==var2){
if(class(demo[[var2]])=="numeric"){
ybreak <- round(range(demo[[var2]],na.rm=TRUE),1)
labs <- as.character(ybreak)}
if(var2=="age2"){labs=c("18-25","71-75")}
if(class(demo[[var1]])=="factor"){

p <- ggplot(demo,aes_string(x=var1,y=var2))+ geom_violin(color="gray",draw_quantiles = c(0.5)) + theme_blank() + ylab("") + theme(axis.text = element_blank(),axis.line.x=element_line(colour = "black"),axis.line.y=element_line(colour = "black"),title=element_text(size=20,hjust = .5))  +
  scale_y_continuous(breaks=ybreak,labels=labs)

star1 <- ifelse(t.test(as.numeric(demo[[var2]]) ~ demo[[var1]])$p.value < 0.05,"*","")
star2 <- ifelse(t.test(as.numeric(demo[[var2]]) ~ demo[[var1]])$p.value < 0.001,"*","")

val <- paste0("t = ",round(t.test(as.numeric(demo[[var2]]) ~ demo[[var1]])$statistic,2),star1,star2)

valstar <- paste0(star1,star2)

if(var2 %in% ordinal){
demo$var2 <- as.numeric(demo[[var2]])
val <- paste0("w = ",round(wilcox.test(y=demo$var2[demo$gender=="F"], x=demo$var2[demo$gender=="M"])$statistic)) 
star1 <- ifelse(wilcox.test(y=demo$var2[demo$gender=="F"], x=demo$var2[demo$gender=="M"])$p.value < 0.05,"*","")
star2 <- ifelse(wilcox.test(y=demo$var2[demo$gender=="F"], x=demo$var2[demo$gender=="M"])$p.value < 0.001,"*","")
valstar <- paste0(star1,star2)
}

p <- p + ggtitle(valstar) + theme(plot.title = element_text(hjust = 0.5))
assign(name_test,p)
p1 <- ggplot() + 
  annotate("text", x = 4, y = 25, size=20, label = val) + 
  theme_void()
assign(paste0(name_test,"val"),p1)
}

if(class(demo[[var1]])=="numeric" & class(demo[[var2]])=="numeric"){

p <- ggplot(demo,aes_string(x=var1,y=var2),color="gray",fill="gray") + geom_smooth(method="lm",color="gray",fill="gray") + theme_blank() + xlab("") + ylab("") + theme(axis.text = element_blank(),axis.line.x=element_line(colour = "black"),axis.line.y=element_line(colour = "black"), title=element_text(size=20,hjust = 0.5)) + scale_x_continuous(breaks=range(demo[[var1]]),labels=round(range(demo[[var1]]),1)) #+scale_y_continuous(breaks=ybreak,labels=labs)
  
if(var1 =="age2"){
ybreak <- round(range(demo[[var1]],na.rm=TRUE),1)
labs <- ybreak
p <- ggplot(demo,aes_string(x=var1,y=var2),color="gray",fill="gray") + geom_smooth(method="lm",color="gray",fill="gray")  + theme_blank() + xlab("") + ylab("") + theme(axis.text = element_blank(),axis.line.x=element_line(colour = "black"),axis.line.y=element_line(colour = "black"), title=element_text(size=20,hjust = 0.5))}
#+ scale_x_continuous(breaks=c(1,11),labels=c("18-25","71-75"))}
  #+scale_y_continuous(breaks=ybreak,labels=labs) + }
  
star1 <- ifelse(cor.test(demo[[var1]], demo[[var2]])$p.value < 0.05,"*","")
star2 <- ifelse(cor.test(demo[[var1]], demo[[var2]])$p.value < 0.001,"*","")
val <- paste0("r = ",round(cor(demo[[var1]], demo[[var2]],use = "pairwise.complete.obs"),2),star1,star2)

valstar <- paste0(star1,star2)
p <- p + ggtitle(valstar) + theme(plot.title = element_text(hjust = 0.5))

assign(name_test,p)}
  
p1 <- ggplot() + 
  annotate("text", x = 4, y = 25, size=20, label = val) + 
  theme_void()
assign(paste0(name_test,"val"),p1)}
print(paste0(var1,var2))
}}



blank <- ggplot() + theme_void()


png("~/Dropbox/mTurk/Figure1.png", width = 1500, height = 1500)
cowplot::plot_grid(vjust = 1, gender, gendergender, genderage2val,genderbmival,genders.cognitive.restraintval,
                   age2, genderage2,age2age2,age2bmival,age2s.cognitive.restraintval,
                   bmi, genderbmi,age2bmi,bmibmi,bmis.cognitive.restraintval,
                   s.cognitive.restraint,genders.cognitive.restraint,age2s.cognitive.restraint,bmis.cognitive.restraint,s.cognitive.restraints.cognitive.restraint,
                   blank, gender_h, age2_h, bmi_h, s.cognitive.restraint_h,
                   nrow = 5,ncol=5,rel_widths = c(0.1,1,1,1,1), rel_heights = c(1,1,1,1,0.1))
dev.off()
```
```{r}

```

# Look at association between choice and three main components for foods: tastiness, healthiness, umami 


# People prefer tastier, less healthy and more savory foods 


```{r, echo=FALSE,results="asis", warnings=FALSE, message=FALSE}

#Now binarize choice
cat("\n\n\\newpage\n")
dat$choice.bin <- ifelse(dat$choice.rating<5,0,1)
dat$choice.bin <- ifelse(dat$choice.rating==5,NA,dat$choice.bin)


##I think for plotting purposes it is nicer to do it by food
avg <- dat %>% group_by(stimulus) %>% summarize_at(c("choice.rating","Healthiness","Tastiness","Umami"),mean,na.rm=TRUE)

avg_count <- dat %>% group_by(stimulus,choice.bin) %>% dplyr::count()
avg_count <- subset(avg_count,!is.na(avg_count$choice.bin))
avg_count <- avg_count %>% pivot_wider("stimulus",names_from=2,values_from=3)
avg_count$prop_choice <- avg_count$`1`/(avg_count$`1`+avg_count$`0`)

avg <- merge(avg,avg_count,by="stimulus")

cat("\n\n\\newpage\n")

BU <- avg

i <- 1
colors <- c("#92D895","sandybrown", "plum")
for(food in c("Healthiness","Tastiness","Umami")){

##missing some foods  
  
labels <- c("kitkat","pizza","strawberries","lox","rice cakes","broccoli","trailmix","skittles")

avg$attribute <- avg[[food]]
avg$label <- ifelse(avg$stimulus %in% labels, avg$stimulus,"")
col_plot <- colors[i]
line_m <- ifelse(i<2.5,"y~x","y ~ x + I(x^2)")
p <- (ggplot(avg, aes(x=attribute,y=prop_choice)) + geom_point(size=4,color=col_plot,fill=col_plot,alpha=0.6) + geom_smooth(method="lm",formula=line_m,size=2,color=col_plot,fill=col_plot,alpha=0.6) + scale_alpha_identity() + ylab("Proportion of selections") + xlab(food) + ylim(0,1) + xlim(-3,3) + ggtitle(food) + geom_text(aes(label=label),nudge_x = 0.1, fontface = "bold",size=6))
ph <- p + theme_blank() + theme(axis.line.x=element_line(color="black",size=2),axis.line.y=element_line(color="black",size=2),text = element_text(size=24), plot.title = element_text(color=col_plot, size=24,face="bold",hjust = .5))

assign(paste0("p",i),ph)
i <- i+1
}

png("~/Dropbox/mTurk/Figure3.png", width = 1500, height = 500)
cowplot::plot_grid(p1,p2,p3, nrow=1)
dev.off()

```
# Summary of choices across all individuals for alternate (i.e., non neutral food choices), healthy choices, high/low-fat choices, RT for SC choices


```{r, echo=FALSE,results="asis", warnings=FALSE, message=FALSE, include=TRUE}
# check linearity of Umami - non-linear effect adds little predictive power 
# regressing out taste and health = linear effect of Umami on choice preference

dat$Umami2 <- dat$Umami^2 
fit2 <- glmer(choice.bin ~ Healthiness + Tastiness + Umami + (1|stimulus) + (1 + Healthiness + Tastiness + Umami | subjectId), data=dat, family="binomial", control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print("prediction of choice")
model_parameters(fit2,keep =c("Healthiness", "Tastiness","Umami"), effects = "fixed") %>% print_md()

fit1 <- glmer(choice.bin ~ Healthiness + Tastiness + Umami + Umami2 + (1|stimulus) + (1 + Healthiness + Tastiness + Umami + Umami2 | subjectId), data=dat, family="binomial", control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print("prediction of choice")
model_parameters(fit2,keep =c("Healthiness", "Tastiness","Umami"), effects = "fixed") %>% print_md()

anova(fit2,fit1)
summary(fit2)

```

## RT analysis
```{r, echo=FALSE,results="asis", warnings=FALSE, message=FALSE, include=TRUE}
dat$choice2 <- dat$choice.rating^2
modRT <- lmer(choice.rt.unscale ~ choice.rating + choice2 + (1 + choice.rating + choice2|subjectId) + (1|stimulus),data=dat, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print(model_parameters(modRT) %>% print_md())

dat$cat_choice <- cut(dat$choice.rating, 
                   breaks=c(seq(0,10,1)), 
                   labels=c(as.character(seq(1,10,1))))

rt <- dat %>% group_by(cat_choice) %>% summarise_at("choice.rt.unscale",mean,na.rm=TRUE)
rt <- subset(rt,!is.na(rt$cat_choice))
ggplot(rt,aes(x=cat_choice,y=choice.rt.unscale)) + geom_bar(stat="identity")

dat$neut.Umami2 <- dat$neut.Umami^2
dat$Umami_diff <- dat$Umami - dat$neut.Umami
dat$Umami2_diff <- dat$Umami2 - dat$neut.Umami2
dat$Healthiness_diff <- dat$Healthiness - dat$neut.Healthiness
dat$Tastiness_diff <- dat$Tastiness - dat$neut.Tastiness


modRTdiff <- lmer(choice.rt.unscale ~ Umami_diff + Umami2_diff + Tastiness_diff + Healthiness_diff + (1 + Umami_diff + Umami2_diff + Tastiness_diff + Healthiness_diff|subjectId) + (1|stimulus),data=dat, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print(model_parameters(modRTdiff) %>% print_md())

ggplot(dat, aes(x=choice.rating,y=choice.rt)) + geom_smooth()
```


# associations with tastiness, healthy, HL-fat, RT, non neutral choice per demo char

```{r, echo=FALSE,results="asis", warnings=FALSE, message=FALSE, include=TRUE}

tab_means <- health_select %>% unique() %>% summarize_at(c(2:8),c(mean,sd),na.rm=TRUE)
table_means <- data.frame()
for(i in 1:7){
val <- paste0(round(tab_means[i],3)," (",round(tab_means[i+7],3),")")
row_val <- as.data.frame(c(gsub("_fn1","", colnames(tab_means[i])),val))
row_val <- transpose(row_val)
colnames(row_val) <- c("var","mean (SD)")
table_means <- rbind(table_means,row_val)              
}

print(table_means)
```


# Generate plots using two-stage estimation (beta coefficients for each individual)
```{r, echo=FALSE,results="asis", warnings=FALSE, message=FALSE}
coef <- coef(fit1)$subjectId
coef$subjectId <- rownames(coef)
colnames(coef) <- c( "(Intercept)","Healthiness_beta","Tastiness_beta","Umami_beta","Umami_quadratic_beta","subjectId" )
single <- merge(single, coef,by="subjectId")

```


```{r, echo=FALSE,results="asis", warnings=FALSE, message=FALSE}
# These are simple associations of demo factors with influence of healthiness, tastiness, umami on choice


cat("\n\n\\newpage\n")
preds <- c("age2", "gender", "bmi","s.cognitive.restraint") #,"education","income")
pred.names <- c("Age (years)","Gender","BMI (kg/m^2)","Cognitive Restraint","Cognitive Restraint x BMI")
colour <- c("sandybrown","#92D895","plum","maroon")
titles <- c("Tastiness","Healthiness","Umami","Umami_quadratic")
outcomes <- c("fit.t","fit.h","fit.u")
outcomes <- c("Tastiness_beta","Healthiness_beta","Umami_beta","Umami_quadratic_beta")
outcome.names <- c("Tastiness Effect","Healthiness Effect","Umami Effect","Umami Effect (quadratic)")

a <- c(-0.5,5)
b <- c(-1.5,1.6)
c <- c(-1.5,1.6)
d <- c(-0.5,0.5)

breaks_a <- seq(-0.5,5,1)
breaks_b <- seq(-1,1.5,0.5)
breaks_c <- seq(-1,1.5,0.5)
breaks_d <- seq(-0.5,0.5,0.2)

lims <- list(a,b,c,d)
breaks <- list(breaks_a,breaks_b,breaks_c,breaks_d)


TAB_lm <- data.frame()
i <- 1

#
for(out in outcomes){
col_out <- colour[i]
single$out <- single[[out]]

j <- 1

for(pred in preds){
single$pred <- single[[pred]]
predname <- pred.names[j]
title <- ""
cat("\n\n\\newpage\n")


p <- plot_template(single,pred = pred,out=out,xlabel = predname,col_out=col_out,ylims=lims[i][[1]],ybreaks=c(breaks[[i]]),title="",yname="Beta")
assign(paste0("p",j),p)


p <- ggplot() + 
  annotate("text", x = 4, y = 25, size=12, label = outcome.names[[i]],color=col_out,fontface =2) + 
  theme_void()
assign(paste0(titles[[i]],"_p"),p)
j <- j+1
}
assign(paste0("plot",i),cowplot::plot_grid(p1,p2,p3,p4,nrow=1,align="vh"))
i <- i+1
}

png("~/Dropbox/mTurk/Figure4.png", width = 1500, height = 1600)
cowplot::plot_grid(Tastiness_p,plot1,Healthiness_p,plot2,Umami_p,plot3,Umami_quadratic_p, plot4,nrow=8,rel_heights =c(0.2,1,0.2,1,0.2,1,0.2,1))
dev.off()

```


```{r}
##interaction plots - median split with BMI

single$bmi_cat <- ifelse(single$bmi > 26.56,1,0)

a <- c(1.5,3)
b <- c(-0.3,0.6)
c <- c(-0.3,.6)
d <- c(-0.1,.1)

lims <- list(a,b,c,d)

j <- 1
for(out in outcomes){
cat("\n\n\\newpage\n")
tit=""
col_out <- colour[j]
single$out <- single[[out]]

xbreaks <- range(round(single$s.cognitive.restraint,0),na.rm=TRUE)
labs <- xbreaks

p <- ggplot(single,aes(x=s.cognitive.restraint,y=out,group=bmi_cat,alpha=bmi_cat)) + geom_smooth(method = "lm",size=3,aes(alpha=bmi_cat),color=col_out,fill=col_out) + scale_alpha_continuous(range=c(0.3,0.8))  + ggtitle(tit) + coord_cartesian(ylim = c(lims[[j]])) + scale_x_continuous(breaks = xbreaks, labels = labs) + xlab("Cognitive Restraint") + ylab("Beta")
p <- p + theme_blank() + theme(axis.line.x=element_line(color="black",size=1),axis.line.y=element_line(color="black",size=1),text = element_text(size=28),plot.title = element_text(color="black", size=14,face="bold",hjust = .5),legend.position = "none")
assign(paste0("p",j),p)
j <- j+1
}
png("~/Dropbox/mTurk/Figure5.png", width = 2000, height = 400)
cowplot::plot_grid(Tastiness_p,Healthiness_p,Umami_p,Umami_quadratic_p, p1,p2,p3,p4,nrow=2,rel_heights =c(0.1,1),ncol = 4)
dev.off()

```

## In fully adjusted models, all demographic characteristics are included
# greater influence of health on choice for: higher restraint, lower bmi, older age
# greater influence of taste for: older age, female, lower restraint
# greater preference for savory for: lower bmi
```{r, echo=FALSE,results="asis", warnings=FALSE, message=FALSE}

## full models
TAB <- data.frame()

cat("\n\n\\pagebreak\n")
print("Do age, bmi, cognitive restraint and gender independently predict influence of healthiness, tastiness, umami?")


form <- paste0("choice.bin ~  (1+ Healthiness + Tastiness + (Umami) + Umami2| subjectId) + Healthiness*s.cognitive.restraint_scale + Healthiness*bmi_scale+ Healthiness*age2_scale+Healthiness*gender_num_scale +Healthiness*income_scale + Umami*s.cognitive.restraint_scale + Umami*bmi_scale+ Umami*age2_scale+Umami*gender_num_scale  + Umami*income_scale + Tastiness*s.cognitive.restraint_scale + Tastiness*bmi_scale+ Tastiness*age2_scale+Tastiness*gender_num_scale + Tastiness*income_scale + Umami2*s.cognitive.restraint_scale + Umami2*bmi_scale+ Umami2*age2_scale+Umami2*gender_num_scale + education_scale*Umami + education_scale*Tastiness + education_scale*Healthiness + (1|stimulus)")
mod <- glmer(form,data=dat, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE),family="binomial")
print(parameters::model_parameters(mod) %>% print_md())

form <- paste0("choice.bin ~  (1+ Tastiness + Healthiness + (Umami) + Umami2| subjectId) + Tastiness + Healthiness + (Umami) + Umami2 + Tastiness*age2_scale+Tastiness*gender_num_scale + Tastiness*bmi_scale*s.cognitive.restraint_scale +  Tastiness*income_scale +  Tastiness*education_scale + Healthiness*age2_scale+Healthiness*gender_num_scale + Healthiness*bmi_scale*s.cognitive.restraint_scale +  Healthiness*income_scale +  Healthiness*education_scale + Umami*age2_scale+Umami*gender_num_scale + Umami*bmi_scale*s.cognitive.restraint_scale +  Umami*income_scale +  Umami*education_scale + Umami2*age2_scale+Umami2*gender_num_scale + Umami2*bmi_scale*s.cognitive.restraint_scale +  Umami2*income_scale +  Umami2*education_scale + (1|stimulus)")
mod_int1 <- glmer(form,data=dat, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE),family="binomial")
print(parameters::model_parameters(mod_int1) %>% print_md())


form <- paste0("choice.bin ~  (1+ Healthiness + Tastiness + (Umami) | subjectId) + Healthiness*s.cognitive.restraint_scale*bmi_scale+ Healthiness*age2_scale+Healthiness*gender_num_scale +Healthiness*income_scale + Healthiness*education_scale+ Umami*s.cognitive.restraint_scale*bmi_scale+ Umami*age2_scale+Umami*gender_num_scale  + Umami*income_scale + Umami*education_scale + Tastiness*s.cognitive.restraint_scale*bmi_scale+ Tastiness*age2_scale+Tastiness*gender_num_scale + Tastiness*income_scale + Tastiness*education_scale + (1|stimulus)")
mod_int <- glmer(form,data=dat, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE),family="binomial")
print(parameters::model_parameters(mod_int) %>% print_md())

form <- paste0("choice.bin ~  (1+ Healthiness | subjectId) + Healthiness*s.cognitive.restraint_scale + Healthiness*bmi_scale+ Healthiness*age2_scale+Healthiness*gender_num_scale +Healthiness*income_scale  + Healthiness*education_scale + (1|stimulus)")
mod1 <- glmer(form,data=dat, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print(parameters::model_parameters(mod) %>% print_md())

form <- paste0("choice.bin ~  (1+ Tastiness| subjectId) + Tastiness*s.cognitive.restraint_scale + Tastiness*bmi_scale+ Tastiness*age2_scale+Tastiness*gender_num_scale +Tastiness*income_scale  + Tastiness*education_scale+  (1|stimulus)")
mod2 <- glmer(form,data=dat, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print(parameters::model_parameters(mod) %>% print_md())

form <- paste0("choice.bin ~  (1+ Umami| subjectId) + Umami*s.cognitive.restraint_scale + Umami*bmi_scale+ Umami*age2_scale+Umami*gender_num_scale +Umami*income_scale  + Umami*education_scale+ (1|stimulus)")
mod3 <- glmer(form,data=dat, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print(parameters::model_parameters(mod) %>% print_md())


```

```{r, echo=FALSE,results="asis", warnings=FALSE, message=FALSE, include=TRUE}
# check linearity of Umami - non-linear effect adds little predictive power 
# regressing out taste and health = linear effect of Umami on choice preference

fit_rt <- lmer(choice.rt.unscale ~ Healthiness + Tastiness + Umami + (1|stimulus) + (1 + Healthiness + Tastiness + Umami | subjectId), data=dat, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print("prediction of choice")
model_parameters(fit_rt,keep =c("Healthiness", "Tastiness","Umami"), effects = "fixed") %>% print_md()

dat$diff_taste <- dat$Tastiness - dat$neut.Tastiness
dat$diff_health <- dat$Healthiness - dat$neut.Healthiness
dat$diff_umami <- dat$Umami - dat$neut.Umami

fit_rt_diff <- lmer(choice.rt.unscale ~ diff_health + diff_taste + diff_umami + (1|stimulus) + (1 + diff_health + diff_taste + diff_umami | subjectId), data=dat, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print("prediction of choice")
model_parameters(fit_rt_diff,keep =c("Healthiness", "Tastiness","Umami"), effects = "fixed") %>% print_md()

ggplot(dat,aes(x=diff_taste,y=choice.rt.unscale)) + geom_smooth(color="sandybrown") + geom_smooth(data=dat,aes(x=diff_health,y=choice.rt.unscale),color="#92D895") + geom_smooth(data=dat,aes(x=diff_umami,y=choice.rt.unscale),color="plum")


fit_rt_c <- lmer(choice.rt.unscale ~ choice.rating + choice2 + (1|stimulus) + (1 + choice.rating +choice2 | subjectId), data=dat, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print("prediction of choice")
model_parameters(fit_rt_c,effects = "fixed") %>% print_md()



```

# Model with BMI*restraint has improved fit
```{r echo=FALSE, message=FALSE, results="asis", warnings=FALSE}

print("Maximally adjusted models with interaction")


form <- paste0("choice.bin ~  (1+ Healthiness + Tastiness + (Umami )| subjectId) + Healthiness*age2_scale+Healthiness*gender_num_scale + Healthiness*income_scale +  Tastiness*income_scale  +  Tastiness*education_scale + Healthiness*education_scale + Umami*education_scale +
Umami*income_scale  + Umami*age2_scale+Umami*gender_num_scale + Tastiness*s.cognitive.restraint_scale*bmi_scale + Umami*s.cognitive.restraint_scale*bmi_scale+ Tastiness*age2_scale+Tastiness*gender_num_scale  +  Healthiness*s.cognitive.restraint_scale*bmi_scale + (1|stimulus)")

mod_full_int <- glmer(form,data=dat, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print(parameters::model_parameters(mod_full_int) %>% print_md())


# best fit is with cog restraint and bmi interaction only
print(anova(mod,mod_full_int))
```

```{r}
cat("\n\n\\newpage\n")
preds <- c("age2", "gender","bmi", "s.cognitive.restraint") #,"education","income")
pred.names <- c("Age","Gender","BMI","Cognitive Restraint")

titles <- c("Healthy Choice Proportion")
outcomes <- c("healthy.choice.prop")

i <- 1
for(pred in preds){
single$pred <- single[[pred]]
xlabel <- pred.names[i]

title <- ""
ylims=c(0,1)
ybreaks=c(0,.25,.50,.75,1.00)
ylabels=c("0",".25",".50",".75","1")
yname="Healthy Choice Proportion"
if(i ==1){tit=title}
else{tit=""}
cat("\n\n\\newpage\n")

out <- single$healthy.choice.prop

p <- plot_template(single,pred = pred,out=out,xlabel = xlabel,col_out="#FDD262",ylims=ylims,ybreaks=ybreaks,title=title,yname=yname)
assign(paste0("p",i),p)
i <- i+1
}

png("~/Dropbox/mTurk/Figure6.png", width = 2000, height = 600)
cowplot::plot_grid(p1,p2,p3,p4,nrow=1,align="vh")
dev.off()
```


```{r}
print("full model - healthy choices")
form <- paste0("healthy.choice.prop ~ gender_num_scale + age2_scale + s.cognitive.restraint_scale + bmi_scale + income_scale + education_scale")
mod <- lm(form, single)
print(model_parameters(mod) %>% print_md())
```

## How does number of self-control trials vary with variables of interest?
# Males  = greater number of SC trials
# Greater restraint  = fewer SC trials
```{r, echo = FALSE, results="asis", warnings=FALSE, message=FALSE}
print("full model - predict number of sc trials")
form <- paste0("n.sctrial_fac ~ gender_num_scale + age2_scale + s.cognitive.restraint_scale + bmi_scale + income_scale + education_scale")
mod <- lm(form, single)
print(model_parameters(mod) %>% print_md())

print("full model to predict self-control")
form <- paste0("sc.rat.factor ~ gender_num_scale + age2_scale + s.cognitive.restraint_scale + bmi_scale + income_scale + education_scale + n.sctrial_fac")
mod <- lm(form, single)
print(model_parameters(mod) %>% print_md())

form <- paste0("sc.rat.factor ~ gender_num_scale + age2_scale + s.cognitive.restraint_scale + bmi_scale + income_scale + education_scale + n.sctrial_fac")
mod <- lm(form, single)
print(model_parameters(mod) %>% print_md())

form <- paste0("sc.approach.prop ~ gender_num_scale + age2_scale + s.cognitive.restraint_scale + bmi_scale + income_scale + education_scale + sc.approach.n")
mod <- lm(form, single)
print(model_parameters(mod) %>% print_md())

form <- paste0("sc.avoid.prop ~ gender_num_scale + age2_scale + s.cognitive.restraint_scale + bmi_scale + income_scale + education_scale + sc.avoid.n")
mod <- lm(form, single)
print(model_parameters(mod) %>% print_md())
```


```{r, echo = FALSE, results="asis", warnings=FALSE, message=FALSE}
sc <- single_f %>% 
  dplyr::select("no.sc.rt","sc.success.rt","sc.fail.rt") %>%  
  summarise_all(list(
    mean = ~mean(., na.rm = TRUE),
    sd = ~sd(., na.rm = TRUE),
    count = ~sum(!is.na(.)),
    se = ~sd(., na.rm = TRUE) / sqrt(sum(!is.na(.)))
  )) %>%
  pivot_longer(everything(), names_to = c("variable", "statistic"), names_sep = "_")  %>%
  pivot_wider(names_from = statistic, values_from = value)
ggplot(sc,aes(x=variable,y=mean)) + geom_bar(stat="identity")
```

```{r}
cat("\n\n\\newpage\n")
preds <- c("age2","gender", "bmi", "s.cognitive.restraint") #,"education","income")
pred.names <- c("Age","Gender","BMI","Cognitive Restraint")
colour <- c("darkblue","#85D4E3")
titles <- c("Number of Conflict Trials","Self-Control Success")

outcomes <- c("n.sctrial_fac","sc.rat.factor")


i <- 1
for(out in outcomes){
j <- 1
col_out <- colour[i]
yname <- titles[i]
for(pred in preds){
single$pred <- single[[pred]]
xlabel <- pred.names[j]  
title <-""

if(i==1){ylims=c(0,40)}else{ylims=c(0,1)}
if(i==1){ybreaks=c(0,10,20,30,40);ylabels=c("0","10","20","30","40")}else{ybreaks=c(0,.25,.50,.75,1.00);ylabels=c("0",".25",".50",".75","1")}

cat("\n\n\\newpage\n")

single$out <- single[[out]]
p <- plot_template(single,pred = pred,out=out,xlabel = xlabel,col_out=col_out,ylims=ylims,ybreaks=ybreaks,title=title,yname=yname)
assign(paste0("p",j),p)

p <- ggplot() + 
  annotate("text", x = 4, y = 25, size=12, label = titles[[i]],color=col_out,fontface =2) + 
  theme_void()
assign(paste0(titles[[i]],"_p"),p)

j <- j+1


}
assign(paste0("plot",i),cowplot::plot_grid(p1,p2,p3,p4,nrow=1,align="vh"))
i <- i+1
}


png("~/Dropbox/mTurk/Figure7.png", width = 1500, height = 1000)
cowplot::plot_grid(`Number of Conflict Trials_p`,plot1,`Self-Control Success_p`,plot2,nrow=4,rel_heights=c(0.2,1,0.2,1))
dev.off()
```


```{r, echo=FALSE, results="asis", warnings=FALSE, message=FALSE}
i <- 1
colors <- c("#92D895", "plum")
for(food in c("Healthiness","Umami")){

labels <- c("kitkat","pizza","strawberries","lox","rice cakes","broccoli","trailmix","skittles")

avg$attribute <- avg[[food]]

avg$label <- ifelse(avg$stimulus %in% labels, avg$stimulus,"")

col_plot <- colors[i]
line_m <- ifelse(i<1.5,"y~x","y ~ x + I(x^2)")
p <- (ggplot(avg, aes(x=attribute,y=Tastiness)) + geom_point(size=4,color=col_plot,fill=col_plot,alpha=0.6) + geom_smooth(method="lm",formula=line_m,size=2,color=col_plot,fill=col_plot,alpha=0.6) + scale_alpha_identity() + ylab("Tastiness") + xlab(food) + ylim(-0.6,1) + xlim(-2,2) + ggtitle(food) + geom_text(aes(label=label), fontface = "bold"))
ph <- p + theme_blank() + theme(axis.line.x=element_line(color="black",size=2),axis.line.y=element_line(color="black",size=2),text = element_text(size=16), plot.title = element_text(color=col_plot, size=24,face="bold",hjust = .5))

assign(paste0("p",i),ph)
i <- i+1
}

cowplot::plot_grid(p1,p2,nrow=1)


avg <- dat %>% group_by(stimulus) %>% summarize_at(c("choice.rating","Healthiness","Tastiness","Umami"),mean,na.rm=TRUE)
avg$label <- ifelse(avg$stimulus %in% labels, avg$stimulus,"")
print("here is plot of tastiness residuals on healthiness")
mod <- lm(Tastiness ~ Umami,avg)
avg$res_tu <- resid(mod)
p <- (ggplot(avg, aes(x=Umami,y=res_tu)) + geom_point(size=3,color="bisque4",fill="bisque4",alpha=0.4) + geom_smooth(method="lm",formula="y ~ x + I(x^2)", size=2,color="bisque4",fill="bisque4",alpha=0.4) + geom_text(aes(label=label)))
print(p + theme_blank() + theme(axis.line.x=element_line(color="black",size=2),axis.line.y=element_line(color="black",size=2),text = element_text(size=16), plot.title = element_text(color=col_plot, size=24,face="bold",hjust = .5))
)

```

```{r, echo=FALSE, results="asis", warnings=FALSE, message=FALSE,fig.show='hold'}
dat$Umami2 <- dat$Umami^2
fit_th_quad <- lmer(Tastiness ~ Healthiness +  Umami + Umami2 + (1|stimulus) + (1 + Healthiness +  Umami + Umami2|subjectId), data=dat, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))

summary(fit_th_quad)
model_parameters(fit_th_quad) %>% print()


fit_th <- lmer(Tastiness ~ Healthiness +  Umami  + (1|stimulus) + (1 + Healthiness +  Umami |subjectId), data=dat, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))

coef_th <- coef(fit_th_quad)$subjectId
coef_th$subjectId <- rownames(coef_th)
colnames(coef_th) <- c( "Intercept_taste","Health_taste_beta","Umami_taste_beta","Umami_taste_quadratic_beta","subjectId" )
single <- merge(single, coef_th,by="subjectId")
cat("\n\n\\newpage\n")
```

```{r}
cat("\n\n\\newpage\n")

print("Maximally adjusted")
form <- paste0("Tastiness ~  (1 + Healthiness + Umami + Umami2 | subjectId) + Healthiness*age2_scale+Healthiness*gender_num_scale + Healthiness*income_scale + Healthiness*education_scale  + Umami*income_scale + Umami*education_scale + Umami*age2_scale+Umami*gender_num_scale +   Umami*s.cognitive.restraint_scale + Umami*bmi_scale+  Healthiness*s.cognitive.restraint_scale + Healthiness*bmi_scale + Umami2*income_scale + Umami2*education_scale + Umami2*age2_scale+Umami2*gender_num_scale + Umami2*s.cognitive.restraint_scale + Umami2*bmi_scale +  (1|stimulus)")
mod_tuh <- lmer(form,data=dat, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print(parameters::model_parameters(mod_tuh) %>% print_md())

```

```{r}
cat("\n\n\\newpage\n")
preds <- c("age2", "gender","bmi","s.cognitive.restraint") #,"education","income")
pred.names <- c("Age","Gender","BMI","Cognitive Restraint")
colour <- c("#92D895","plum","maroon")
titles <- c("Healthiness","Umami","Umami2")

outcomes <- c("Health_taste_beta","Umami_taste_beta","Umami_taste_quadratic_beta")
outcome_names <- c("Healthiness Effect","Umami Effect (linear)","Umami Effect (quadratic)")

lims <- c(-1,1)

ybreaks=c(-1.0,-0.5,0.0,0.5,1.0)
ylabels=c("-1.0","-0.5","0","0.5","1.0")

ybreaks_u=c(-0.6,-0.3,0.0,0.3,0.6)
lims_u <- c(-0.6,0.6)
ylabels_u=c("-0.75","-0.25","0","0.25","0.75")

i <- 1
for(out in outcomes){
if(i > 1) {ybreaks <- ybreaks_u; lims <- lims_u}
col_out <- colour[i]
single$out <- single[[out]]
j <- 1
title <- ""

cat("\n\n\\newpage\n")
for(pred in preds){
single$pred <- single[[pred]]
predname <- pred.names[j]

p <- plot_template(single,pred = pred,out=out,xlabel = predname,col_out=col_out,ylims=lims,ybreaks=ybreaks,title=title,yname="Beta")
assign(paste0("p",j),p)



p <- ggplot() + 
  annotate("text", x = 4, y = 25, size=12, label = outcome_names[[i]],color=col_out,fontface =2) + 
  theme_void()
assign(paste0(titles[[i]],"_p"),p)
j <- j+1

}
assign(paste0("plot",i),cowplot::plot_grid(p1,p2,p3,p4,nrow=1))
i <- i+1
}


png("~/Dropbox/mTurk/Figure9.png", width = 1500, height = 1200)
cowplot::plot_grid(Healthiness_p,plot1,Umami_p,plot2,Umami2_p,plot3,nrow=6,rel_heights =c(0.2,1,0.2,1,0.2,1))
dev.off()
```



# here looking at hXt correlation and SC, with selection of healthier foods, high-fat foods, low-fat foods, influence of health on choice, and SC RTs
```{r, echo = FALSE, results="asis", warnings=FALSE, message=FALSE}

form <- "healthy.choice.prop ~ scale(Health_taste_beta,center=TRUE) + scale(sc.rat.factor,center=TRUE)"
mod <- lm(form, single)
cat("\n\n\\newpage\n")
print(paste0(out, " on ",var))
print(model_parameters(mod) %>% print_md())

form <- "healthy.choice.prop ~ scale(Umami_taste_beta,center=TRUE)" # #scale(sc.rat.factor,center=TRUE)
mod <- lm(form, single)
cat("\n\n\\newpage\n")
print(paste0(out, " on ",var))
print(model_parameters(mod) %>% print_md())

form <- "healthy.choice.prop ~ scale(Umami_taste_quadratic_beta,center=TRUE) + scale(Umami_taste_beta,center=TRUE) +  scale(Health_taste_beta,center=TRUE) + scale(sc.rat.factor,center=TRUE)"
mod <- lm(form, single)
cat("\n\n\\newpage\n")
print(paste0(out, " on ",var))
print(model_parameters(mod) %>% print_md())

form <- "healthy.choice.prop ~ scale(Umami_taste_quadratic_beta,center=TRUE) + scale(Umami_taste_beta,center=TRUE)"
mod <- lm(form, single)
cat("\n\n\\newpage\n")
print(paste0(out, " on ",var))
print(model_parameters(mod) %>% print_md())

cor.test(single$sc.rat.factor,single$Health_taste_beta)
```

```{r}

xbreaks <- range(round(single$sc.rat.factor,0),na.rm=TRUE)
labs <- xbreaks
j <- 3
ylims=c(0,1)
ybreaks=c(0,.25,.50,.75,1.00)
ylabels=c("0",".25",".50",".75","1")

p1 <- plot_template(single,"sc.rat.factor","healthy.choice.prop",col_out = "#FDD262",ylims = ylims,ybreaks = ybreaks,yname = "Proportion of healthy choices",xlabel = "Self-Control Success")

p2 <- plot_template(single,"Health_taste_beta","healthy.choice.prop",col_out = "#FDD262",ylims = ylims,ybreaks = ybreaks,yname = "Proportion of healthy choices",xlabel = "Healthiness-Tastiness Beta")

png("~/Dropbox/mTurk/Figure10.png", width = 750, height = 400)
cowplot::plot_grid(p1,p2,nrow=1)
dev.off()

plot_template(single,"sc.rat.factor","Health_taste_beta",col_out = "#FDD262",ylims = ylims,ybreaks = ybreaks,yname = "Healthiness-Tastiness Beta",xlabel = "Self-Control Success")

```

## RT analysis

## what happens to RT on successful vs unsuccessful self-control trials
## largely effects of cognitive restraint - faster to make healthier choices and to use SC (relative to no SC)
```{r echo=FALSE, message=FALSE, results="asis", warnings=FALSE}
cat("\n\n\\newpage\n")
print("Maximally adjusted models")


## here is regular RT model - compare SC RT and no SC RT over demographic groups
no_sc <- single[,c("subjectId","rt_no_sc","bmi_scale","gender_num_scale", "age2_scale", "s.cognitive.restraint_scale", "income_scale","education_scale")]
sc <- single[,c("subjectId","rt_sc","bmi_scale","gender_num_scale", "age2_scale", "s.cognitive.restraint_scale","income_scale","education_scale")]
colnames(sc)[2] <- "rt"
colnames(no_sc)[2] <- "rt"
sc$trial <- "sc"
no_sc$trial <- "no_sc"

SC_RT <- rbind(sc,no_sc)
modRT <- lmer(rt ~ trial*bmi_scale + trial*s.cognitive.restraint_scale + trial*age2_scale + trial*gender_num_scale + trial+income_scale + trial*education_scale + (1|subjectId),data=SC_RT, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print(model_parameters(modRT) %>% print_md())


modRT <- lmer(rt ~ trial*bmi_scale + trial*s.cognitive.restraint_scale*bmi_scale + trial*age2_scale + trial*gender_num_scale + trial+income_scale + trial*education_scale + (1|subjectId),data=SC_RT, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5), calc.derivs = FALSE))
print(model_parameters(modRT) %>% print_md())


single$diff <- (single$rt_sc - single$rt_no_sc)/1000
i <- 1
for(pred in preds){
single$pred <- single[[pred]]
predname <- pred.names[i]
single$out <- single$diff
p <- plot_template(dataset = single,pred = pred,out="diff",col_out = "bisque",yname = "Effect of self-control on RT (s)",xlabel = predname,ylims = c(-2.5,2.5),ybreaks=c(-2,-1,0,1,2),title="")
assign(paste0("p",i),p)
i <- i+1
}

png("~/Dropbox/mTurk/Figure8.png", width = 1500, height = 400)
cowplot::plot_grid(p1,p2,p3,p4,nrow=1)
dev.off()
# plot SC bins?
```

## average kcals of reference item do not vary by demographic group


```{r, echo = FALSE, results="asis", warnings=FALSE, message=FALSE,include=FALSE}
# diffs in ref food kcal by demo chars
form <- paste0("neut.Total.kcal ~ gender_num_scale + age2_scale + s.cognitive.restraint_scale + bmi_scale + income_scale + education_scale")
mod <- lm(form, single)
print(model_parameters(mod)) %>% print_md()
```


## here are the DDM outputs for the best-fitting model

# additional info is that non-decision time and choice bounds (evidence needed to make choice) are larger for older adults, smaller for those w. greater restraint (maybe indexing easier selection of healthier choice). weights of health and taste on choice are consistent with findings above.

##table summarizing choices, RTs, healthy choices, H/L fat

```{r, echo = FALSE, results="asis", warnings=FALSE, message=FALSE}
cat("\n\n\\newpage\n")
tv_ests <- read.csv("~/Dropbox/mTurk/DDMparams_fitted.csv")[-c(1:7),]
tv_ests$n <- stringr::str_split_i(tv_ests$X,"\\[",2)
tv_ests$n <- gsub("]","",tv_ests$n,fixed=TRUE)
tv_ests$X <- stringr::str_split_i(tv_ests$X,"\\[",1)
wide_ests <- tv_ests %>% pivot_wider(n,names_from="X",values_from="Mean")


subs <- read.csv("~/Dropbox/mTurk/DDM_sublist.csv")
wide_ests$sub <- subs$subjectId

wide_ests <- merge(single, wide_ests,by.x="subjectId",by.y="sub")
preds <- c("gender", "age2", "bmi", "s.cognitive.restraint")
outcomes <- c("b1.p","b2.p","b3.p","time_health.p","alpha.p","theta.p","bias")

wide_ests$time_health.p <- wide_ests$time_health.p*1000
#wide_ests$time_health.p <- abs(wide_ests$time_health.p)

TV <- data.frame()
for(out in outcomes){
wide_ests$out <- wide_ests[[out]]
m <- lm(out ~ gender_num_scale + age2_scale + s.cognitive.restraint_scale+bmi_scale + income_scale + education_scale,wide_ests)# + income_scale + education_scale,tv_ests)
print(paste0(out," ~ s.cognitive.restraint + bmi + age2 + gender"))
print(model_parameters(m) %>% print_md())
print(ggplot(wide_ests,aes(x=s.cognitive.restraint,y=out)) + geom_point()) + geom_smooth(method="lm")
}


```


```{r}
#Figures


preds <- c("age2", "gender", "bmi","s.cognitive.restraint") #,"education","income")
pred.names <- c("Age","Gender","BMI","Cognitive Restraint")
colour <- c()
colours <- c("sandybrown", "#92D895", "slateblue2", 
            "#C9ADA7", "lightcoral")
       

outcomes <- c("b1.p", "b2.p", "time_health.p","alpha.p", "theta.p")
outcome.names <- c("Tastiness Effect","Healthiness Effect","Delay of Healthiness relative to Tastiness and Umami", "Choice Boundary","Non-Decision Time")

axislab <- c("Beta","Beta","Time (s)","Bound","NDT")
limits <- list(c(0,1),c(-.5,.5),c(25,50),c(0,3),c(0,2))


TAB_lm <- data.frame()
i <- 1

#
for(out in outcomes){

col_out <- colours[i]
wide_ests$out <- wide_ests[[out]]
ylims <- c(limits[[i]])
y <- axislab[i]
ybreaks=seq(ylims[1],ylims[2],(ylims[2]-ylims[1])/4)
title <-outcome.names[i]
j <- 1

for(pred in preds){


if(i ==1){tit=title}
  else{tit=""}
cat("\n\n\\newpage\n")

wide_ests$pred <- wide_ests[[pred]]
predname <- pred.names[j]

p <- plot_template(dataset = wide_ests,pred = pred,out=out,col_out = col_out,title=title,xlabel = predname,ylims=ylims,ybreaks=ybreaks,yname=y)
assign(paste0("p",j),p)
j <- j+1
}
assign(paste0("plot",i),cowplot::plot_grid(p1,p2,p3,p4,nrow=1))
i <- i+1
}

i <- 1
for(out in outcomes){
p <- ggplot() + 
  annotate("text", x = 6, y = 25, size=12, label = outcome.names[[i]],color=colours[i],fontface =2) +
  theme_void()
assign(paste0(out,"_p"),p)
i <- i+1
}
#title <- cowplot::plot_grid(,nrow=1)

##int 
png("~/Dropbox/mTurk/Figure11_p1.png", width = 2000, height = 1500)
cowplot::plot_grid(b1.p_p,plot1,b2.p_p,plot2,time_health.p_p,plot3, nrow=6,rel_heights =c(0.1,1,0.1,1,0.1,1))
dev.off()


png("~/Dropbox/mTurk/Figure11_p2.png", width = 2000, height = 1000)
cowplot::plot_grid(alpha.p_p,plot4,theta.p_p,plot5, nrow=4,rel_heights =c(0.1,1,0.1,1))
dev.off()

```
